---
title: "Exploratory Shiny"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(png)
library(knitr)
```

## Exploratory dfSummary

This project aims to use summarytools on shiny and allowing a reactive model with datatable filters. It's also possible to download a pdf of summarytools view function.

The idea is quite simple, upload the data and explore it by filtering data and checking the result on the summary tab.

I find this helpful to have a quick look at the data and its attributes.

**All credits on file input sidebar goes to SachaEpskamp: https://gist.github.com/SachaEpskamp/5796467 who delivered the best solution for a vast majority of r packages on input files**

There is also a function to use it locally, this might be useful for large datasets.

Category: Shiny extensions
Keywords: Summarytools, DT, reactive
Shiny app: https://eduardodudu.shinyapps.io/ShinyDfSummary/
Repo: https://github.com/Eduardodudu/ExploratoryShiny
RStudio Cloud: https://rstudio.cloud/project/959448

Full Example:

```{r, warning=F, include=T, echo=F, fig.align='center'}
img1_path <- "./Images/dfSummary.png"
img1 <- readPNG(img1_path, native = TRUE, info = TRUE)
include_graphics(img1_path, dpi = 50)
```
  
